---
title: "Assignment 2"
format:
  html:
    embed-resources: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = TRUE, 
                      fig.height = 3, 
                      fig.width  = 6,
                      fig.align  = "center")
ggplot2::theme_set(ggplot2::theme_bw())
library(tidyverse)
```

## Instructions

Complete the following exercises **using only the tidyverse packages** (e.g., `dplyr`, `tidyr`, `ggplot2`, `readr`, `stringr`, `forcats`, `lubridate`, `purrr`, etc.)

**Important:** This assignment is intended to assess your proficiency with the **tidyverse**. Solutions that use **base R** or **packages outside the tidyverse** to solve the problems will **not receive credit** unless explicitly permitted in the question.

1.  Load the necessary **tidyverse** libraries.
2.  Answer each question in a separate R code chunk.
3.  Provide a detailed explanation of your approach for each solution.
4.  Render your R Markdown document to an HTML file.
5.  Submit the rendered HTML file to Canvas.

# Question:

- **Task 1: Read data using a relative path**

```{r}
college_data <- read.csv("~/Documents/Data_413/collegedata.csv")
```

The first thing I did was download the data from the canvas page into my computer. Then I saved the data into my Data_413 so that it will be easy to to access the data. Then I set the working directory to be the same folder Data_413. Finally, I wrote the simple code above to pull the data into my R from my folder so that I can work with it.

- **Task 2:Determine rows and columns**

```{r}
glimpse(college_data)
```

I used the \`glimpse()\` function from the dplyr package to examine the structure of the dataset. The output shows the total number of rows and columns in \`college_data\`. The rows represent the observations in the dataset, while the columns represent the variables.

- **Task 3: Use tidyverse to select INSTNM, SAT_AVG, and ADM_RATE**

```{r}
college_data |>
  select(INSTNM, SAT_AVG, ADM_RATE) |>
  slice_head(n = 10)

```

I used the \`select()\` function from dplyr to choose the three variables requested: \`INSTNM\`, \`SAT_AVG\`, and \`ADM_RATE\`. This removes the other variables from the displayed dataset while keeping the information needed for this question.

- **Task 4: Create a scatterplot for SAT_AVG and ADM_RATE (Remove NA)**

```{r}
college_data |>
  drop_na(SAT_AVG, ADM_RATE) |>
  ggplot(aes(x = SAT_AVG, y = ADM_RATE)) +
  geom_point()
```

First I called on the data frame then I used a pipe to run the rest of the code lines. I used \`drop_na()\` to remove observations with missing values for \`SAT_AVG\` or \`ADM_RATE\`. I then used \`ggplot()\` and \`geom_point()\` to create a scatterplot. \`SAT_AVG\` is placed on the x-axis and \`ADM_RATE\` is placed on the y-axis so that I can examine the relationship between average SAT scores and admission rates.
